\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{xcolor}

\title{SE 3XA3: Problem Statement\\Big Two}

\author{Team 06, Team Name: Aplus^3
		\\ Senni Tan, tans28
		\\ Manyi Cheng, chengm33
		\\ Jiaxin Tang, tangj63
}
\date{}

\begin{document}

\begin{table}[h!]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Jan 28 & Manyi Cheng & Initial Draft\\
Jan 28 & Senni Tan & Edited the second question in the problem statement\\
Jan 29 & Jiaxin Tang & Updated the first question\\
Apr 3 & Jiaxin Tang & \textcolor{red}{Revision 1.0 updated}\\
Apr 4 & Manyi Cheng & \textcolor{red}{Revision 1.0 updated}\\
Apr 11 & Senni Tan & \textcolor{red}{Revision 1.0 updated}\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\section{What problem are you trying to solve?
}
Many people enjoys playing card games for entertainment. BigTwo is one of the most popular card games in Asia, especially in China. As game developers, we want to create a new platform for people who would like to play BigTwo solely through a website. We are trying to re-implement the original BigTwo for web browsers. \textcolor{red}{Also, we will change the original project from a multi-player mode to a single-player mode.}

\section{Why is this an important problem?}
Big Two is a very popular game in Asia but not many people know about it in North America. The Big Two card game requires four people to play so people who love playing Big Two in North America may not gather enough people to play the card game, or, they want to play this game with their friends but their friends do not know how to play. Our recreation will allow the player to play the game alone with computer \textcolor{red}{bots} when he can not gather enough people, especially under the pandamic situation. Additionally, our recreation will also be able to provide chances for a beginner to practice the card playing skills or strategies in the single-player mode of the game.



\section{What is the context of the problem you are solving?}

The goal of this project is to re-implement the classic LAN party game BigTwo as a browser game with accurate rules and appropriate documentation. Browser games are portable and can be played on multiple different devices, \textcolor{red}{major web browsers after 2015}, and operating systems. Stakeholders of the game are individuals or organizations that would have an interest in the release of the BigTwo game, including \textcolor{red}{the clients, who are the teaching assistants and professor of this course}, developers, players, game journalists, as well as Entertainment Software Association of Canada, which holds the authority to regulate the content of our project.


\end{document}

